\documentclass[letterpaper,11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[english]{babel}
\usepackage[sfdefault,light]{roboto}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\graphicspath{ {./} }

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{gray}\titlerule \vspace{-5pt}]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Commands                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\sectionElementsListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\sectionElementsListEnd}{\end{itemize}}

\newcommand{\bulletItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\formattedBulletItem}[2]{\bulletItem{#1}{#2}\vspace{-4pt}}

\newcommand{\sectionElement}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
  }
  
\newcommand{\bulletListStart}{\begin{itemize}}
\newcommand{\bulletListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\stacklist}[1]{\color{gray}\scriptsize{
  Stack: #1
}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header                                                                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}

  \begin{tabular}{@{}l@{$\ $}l@{}}%
    \multicolumn{2}{l}{\textbf{\Large Tomasz Radziejewski}}\\
    Location: & Gdańsk, Poland \\
    Mobile: & (omitted for web) \\
    E-mail: & \href{mailto:tomasz@radziejewski.pl}{tomasz@radziejewski.pl} \\
  \end{tabular} &

  \begin{tabular}{@{}l@{$\ $}l@{}}%
    \multicolumn{2}{l}{}\\
    Web: & \href{https://radziejewski.pl/}{radziejewski.pl} \\
    Github: & \href{https://github.com/tradziej/}{tradziej} \\
    LinkedIn: & \href{https://www.linkedin.com/in/radziejewski/}{radziejewski} \\
  \end{tabular}

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Summary                                                                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
  Experienced Software Engineer specializing in software solutions for business.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
 \sectionElementsListStart
    \formattedBulletItem{Programming Languages}{Ruby, JavaScript, HTML, CSS, SQL}

    \formattedBulletItem{Libraries \& Frameworks}{Ruby on Rails, RSpec, Minitest, React, Ember.js, Git, Docker}

    \item{
    \textbf{}{Proficient in a variety of programming aspects, such as design patterns, version control, code documentation, code reviews,
      test-driven development, continuous integration, continuous delivery and agile project management. \vspace{-2pt}}
    }\vspace{-4pt}
 \sectionElementsListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience                                                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
  \sectionElementsListStart
    \sectionElement
    {Localistico}{Remote}
    {Software Engineer}{May 2019 - ...}
      \bulletListStart
      \bulletItem{{\href{https://localistico.com}{Localistico.com}}}
        {Currently working on the backend for an app used by brands like Orange and Starbucks to manage and track how their locations look across different
        mapping and platforms, from Google Maps to Yelp. Built features like extended attributes for Google My Business or roles \& permissions.
        Experience with fast-paced, high intensity environments.
          \\ \stacklist{Ruby, Ruby on Rails, PostgreSQL, Minitest, Heroku, Docker}}
    \bulletListEnd

    \sectionElement
      {Self-employed}{Remote}
      {Software Engineer}{Jan 2016 - Apr 2019}

      \bulletListStart
        \bulletItem{{\href{https://getbuzz.io/start}{Getbuzz.io}}}
          {Developed a Ruby on Rails backend as well as a frontend using Ember.js JavaScript framework.
            Took ownership of the codebase and successfully designed and developed diverse features such as: multi-author
            blogging feature, invite feature for various social networks, connect feature for software users,
            a payments feature, design of database models and queries, a Docker-based deployment environment,
            as well as frontend JavaScript components.
            \\ \stacklist{Ruby, Ruby on Rails, JavaScript, Ember.js, HTML, CSS, PostgreSQL, RSpec, CircleCI, AWS, Docker}}
      \bulletListEnd

    \sectionElement
      {Codahead}{Kraków, Poland}
      {Software Engineer}{Apr 2013 - Dec 2015}

      \bulletListStart
        \bulletItem{\href{https://spinlister.com}{Spinlister.com}}
          {Peer-to-peer bike rental platform. Involved in improving testability, refactoring and maintenance of
            legacy code. Worked with international teams.
            \\ \stacklist{Ruby, Ruby on Rails, JavaScript, Backbone.js, HTML, CSS, PostgreSQL, RSpec, CircleCI, Heroku}}

        \bulletItem{\href{https://listables.com}{Listables.com}}
          {Ember.js frontend for a web application used for collaboratively creating, sharing and tracking checklists.
            \\ \stacklist{JavaScript, Ember.js, HTML, CSS, Apache Cordova}}

        \bulletItem{\href{https://appetizeapp.com}{Appetizeapp.com}}
          {Point of Sale \& Ordering Solutions. Involved in features such as integration with external systems,
            as well as bug fixing.
            \\ \stacklist{PHP, JavaScript, HTML, CSS, MySQL}}
      \bulletListEnd
  \sectionElementsListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education                                                                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
  \sectionElementsListStart
    \sectionElement
      {Tadeusz Kościuszko Cracow University of Technology}{Kraków, Poland}
      {Master of Science in Applied Computer Science}{2011 -- 2013}

    \sectionElement
      {AGH University of Science and Technology}{Kraków, Poland}
      {Bachelor of Science in Computer Science and Econometrics}{2008 -- 2011}
  \sectionElementsListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal Projects                                                            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}
  \sectionElementsListStart
    \formattedBulletItem{\href{https://github.com/tradziej/najnowsze.xyz}{Najnowsze.xyz}}
      {A lightweight, serverless Wykop client.}

    \formattedBulletItem{Aboutme GraphQL API}
      {Serverless microservice on AWS Lambda providing information about recently played track from Spotify,
      posts from Instagram, distance jogged from Endomondo, etc.}
  \sectionElementsListEnd

\end{document}